
\chapter*{Preface}

This thesis concludes the work in \textit{TTK 4900 - Engineering Cybernetics, Masters Thesis}. The idea of an Internet of Things chessboard came from Microchip Technology inc., but the design and implementation has been done by me.\newline

Several programs have been utilized during the thesis. Atmel Studio 7.0 has been used to program the firmware for all devices. Altium Designer to layout and design the printed circuit boards (PCB). Inkscape to design the enclosure layout. Vim has been used to program the web services, running on the open source NGINX platform.\newline

I would like to thank my supervisor, Professor Geir Mathisen for his guidance and insight during the thesis. Moreover i would like to thank my co-supervisor at Microchip Technology inc., Alexander Eide Thorstensen for his motivation and helpfulness throughout the whole process.\newline

A special thanks goes out to Carlo Kriesi at TrollLabs NTNU for lending out their equipment and helping in the process of laser cutting the box for the finished product. Omega Verksted for helping in the design process with invaluable review of the PCBs, saving a lot of head-acne.\newline

Lastly I would like to thank my girlfriend, Laura Garcia Calvo for her understanding, emotional support and patience these last months.\newline

\noindent\begin{tabular}{ll}
&\\
\makebox[3in]{\hfill} & \makebox[2in]{\hrulefill}\\
&Johan Vårlid\\% adds space between the two sets of signatures
& \today\\
\end{tabular}
\clearpage